h1. Kinetic3

Welcome to the Kinetic3 source repository. What is Kinetic? It aims to be a C# 3D Engine that is cross platform (Mono/.Net 3.5+). Currently OpenTK sits between K3 and OpenGL/AL/CL and it has no DirectX support (if you write me a renderer I will include it).

I have decided to change from Mecurial/Bitbucket to Git/Github for this version. I like both and I dont see why not use both?

K3 is a rewrite of the second version of the Kinetic project that sits in "Bitbucket":https://bitbucket.org/openecho/kinetic-sharp. Basically, I do not know a lot about writing a 3D Engine so I make a lot of mistakes. K2 like K1 have basically come to a halt because I have painted myself into a corner and its time that I refactor to a new codebase that I can manage. K2 is still pretty cool, but really it lacks the depth required for a decent engine.

h2. Goals for K3

I am positive there will be a K4 so I dont get to stressed about this, but I would like,

# Comprehensive Scene Management
# Frustum Culling (Carry over from K2-008)
# Shader Support
# Skybox niceness
# An orthongonal overlay and management for it

This version should cross the bridge for multiple renderers nicely on a single display.

h3. Contact

Doing this kind of thing is a lonely journey - its funny, there are 1000's of pimply faced kids wanting to create the next MMO or some such dream. This is good for them, but it really just adds noise to any forum or search for people with similar interests. 

Perhaps I am just another one?

Anyway, If you have an interest in 3D engines or some goals to achieve then please let me know. 
